\section{Experimental Setup}
The local smoke configuration runs without paid APIs using deterministic MockLLM-compatible agents. API-backed adapters use LiteLLM-compatible provider settings and are launched through the resumable streaming runner with \texttt{--resume} and configurable \texttt{--max-workers}. Missing credentials are skipped when \texttt{skip\_missing\_credentials: true}, which keeps artifact smoke tests reproducible on machines without API access.

Experiments measure criterion inference, spec-first execution, own-spec violations, verifier robustness, and model scaling. Statistical reporting uses task-level bootstrap confidence intervals and domain/difficulty stratification. Main execution claims should use rows whose diagnostics report \texttt{execution\_mode=tool\_plan\_executor}; reference-harness paths are retained only for validation and smoke checks.

\subsection{Planned Evaluation Matrix}

The artifact separates deterministic smoke tests from API-backed paper runs. Smoke tests are intended for every checkout and continuous integration. The current completed live-model paper run uses the \texttt{topconf\_deepseek\_toolplan\_full} suite on the topconf-4 test split.

\begin{table}[tbp]
\centering
\small
\begin{tabularx}{\linewidth}{lX X X}
\toprule
Suite & Split & Agents & Models \\
\midrule
Smoke & dev & Heuristic, Spec-first & Mock \\
DeepSeek tool-plan full & test & Direct, Plan-first, Spec-first & Chat, Reasoner, V4 Flash, V4 Pro \\
Oracle reference upper bound & test & Oracle-spec & Mock/reference replay \\
Token-matched DeepSeek & test & Token-matched Direct, Plan-first, Spec-first & V4 Flash, V4 Pro \\
China-provider cross-family slice & test & Direct, Plan-first, Spec-first & DeepSeek, Qwen, GLM, Kimi (configured; pending keys) \\
\bottomrule
\end{tabularx}
\caption{Experiment suites summarized from \texttt{configs/experiments.yaml}; pending suites are configured but not used for claims.}
\end{table}

\subsection{Baselines and Ablations}

Direct runs execute with only implicit completion checks. Plan-first elicits action order and dependencies before acting. Spec-first explicitly elicits completion criteria and a DoneSpec before acting. All three protocols feed a structured tool-call plan into the same environment executor. Oracle-spec replays the repaired gold reference trace with the gold verifier and is treated as a reference upper bound for corpus validity, not as a live model capability estimate. Paper claims should use live-model rows and report token-matched controls before attributing raw task-success differences to specification grounding.

\begin{table}[tbp]
\centering
\small
\begin{tabularx}{\linewidth}{lX X}
\toprule
Ablation & Purpose & Paper status \\
\midrule
Direct vs. Plan-first & Separate planning from completion semantics & DeepSeek full reported \\
Plan-first vs. Spec-first & Test the value of explicit done criteria & DeepSeek full reported \\
Spec-first vs. Oracle reference & Confirm repaired corpus upper bound & Reported as reference replay \\
Near-miss mutation families & Stress-test verifier robustness & Full breakdown reported \\
Token-matched prompting & Control for prompt length & Full DeepSeek run reported \\
Repeated-attempt pass@k & Estimate reliability rather than one-shot success & Pass@3 reported from full run \\
China-provider cross-family model slice & Check that DoneBench effects are not DeepSeek-family artifacts & Configured; pending Qwen/GLM/Kimi keys \\
\bottomrule
\end{tabularx}
\caption{Completed and configured ablations relevant to the current paper claims.}
\end{table}

\subsection{API Run Protocol}

Hosted-model results should report provider, model identifier, access date, decoding parameters, retries, and trial count. Runs should be launched only after the relevant environment variable is set in the active shell. Missing credentials are skipped when \texttt{skip\_missing\_credentials: true}, which prevents smoke reproduction from failing on machines without API access.
