\section{Results}
The current full tool-plan run covers the held-out topconf-4 test split with 500 tasks, 3 agent protocols, 4 DeepSeek-family models, and 3 trials per model-agent-task cell, for 18,000 API trials. Each model-agent cell has \(n=1500\) trials. The run predates the later full-corpus reference-artifact repair, so we treat it as the main completed model run for analyzing the specification-to-execution gap while separately reporting repaired-corpus strict validation and oracle-reference results. Artifacts are under \texttt{reports/full\_runs/runs/topconf\_deepseek\_toolplan\_full/}; refreshed paper tables are under \texttt{paper/tables/}.

\begin{table}[h]
\centering
\begin{tabular}{lllrrrr}
\toprule
Model & Agent & Parse & CC-F1 & DoneSpec valid & Near-miss detect & Task success \\
\midrule
DeepSeek Chat & Direct & 100.0 & 37.1 & 100.0 & 60.0 & 0.0 \\
DeepSeek Chat & Plan-first & 100.0 & 43.9 & 99.9 & 59.9 & 0.0 \\
DeepSeek Chat & Spec-first & 100.0 & 52.6 & 19.9 & 12.0 & 0.0 \\
DeepSeek Reasoner & Direct & 95.7 & 45.7 & 100.0 & 60.0 & 0.0 \\
DeepSeek Reasoner & Plan-first & 98.5 & 47.3 & 99.3 & 59.6 & 0.0 \\
DeepSeek Reasoner & Spec-first & 94.9 & 56.4 & 82.9 & 49.7 & 5.2 \\
DeepSeek V4 Flash & Direct & 98.9 & 44.5 & 99.9 & 60.0 & 0.0 \\
DeepSeek V4 Flash & Plan-first & 98.2 & 47.9 & 99.6 & 59.8 & 0.0 \\
DeepSeek V4 Flash & Spec-first & 94.9 & 56.7 & 84.2 & 50.5 & 6.0 \\
DeepSeek V4 Pro & Direct & 91.9 & 57.1 & 96.3 & 57.8 & 0.0 \\
DeepSeek V4 Pro & Plan-first & 93.8 & 56.6 & 91.3 & 54.8 & 0.0 \\
DeepSeek V4 Pro & Spec-first & 71.9 & 65.0 & 66.2 & 39.7 & 4.5 \\
\bottomrule
\end{tabular}
\caption{Full DeepSeek tool-plan results. Values are percentages; bootstrap confidence intervals are in \texttt{paper/tables/main\_results\_full\_toolplan.csv}.}
\end{table}

The central pattern is a specification-to-execution gap. Spec-first improves criterion completion F1 for every model family member, but nonzero task success remains limited and low. Direct and plan-first produce no successful task completions despite high syntactic DoneSpec validity. Spec-first reaches 6.0\% success for V4 Flash, 5.2\% for Reasoner, 4.5\% for V4 Pro, and 0.0\% for Chat. DeepSeek V4 Pro obtains higher spec-first CC-F1 than V4 Flash (65.0 vs. 56.7), but lower spec-first task success (4.5 vs. 6.0) and lower near-miss detection (39.7 vs. 50.5). We therefore avoid leaderboard claims: a model can articulate more gold-like criteria while producing brittle or poorly operationalized verifiers.

\begin{table}[h]
\centering
\begin{tabular}{lrrrr}
\toprule
Domain & Flash success & Pro success & Flash CC-F1 & Pro CC-F1 \\
\midrule
Calendar & 3.0 & 2.3 & 49.2 & 59.5 \\
Email & 13.0 & 10.0 & 58.3 & 64.3 \\
Sheet/database & 0.0 & 0.0 & 60.1 & 67.1 \\
CRM/workflow & 14.0 & 9.7 & 59.4 & 66.2 \\
File/document & 0.0 & 0.3 & 56.7 & 68.0 \\
\bottomrule
\end{tabular}
\caption{Spec-first domain-stratified V4 results from the full tool-plan run. Values are percentages; full domain tables are in \texttt{paper/tables/domain\_results\_full\_toolplan.csv}.}
\end{table}

\subsection{Reliability and Controls}

The 3-trial full run allows pass@3 reliability analysis. For spec-first, pass@3 is higher than pass@1 but still low: 14.4\% for V4 Flash, 11.8\% for Reasoner, 11.6\% for V4 Pro, and 0.0\% for Chat. Success consistency is 86.0--88.6\% for the nonzero spec-first cells, which mostly reflects repeated failure rather than stable success. A repaired-corpus oracle-reference run solves 500 / 500 test tasks with CC-F1 99.0\%, near-miss detection 100.0\%, task success 100.0\%, and self-violation 0.0\%, confirming that the repaired gold references and graders are executable.

The token-matched DeepSeek ablation runs one trial per task with Direct, Plan-first, and Spec-first prompts padded to the same 3,200-character specification budget. Under this control, task success is no longer a spec-first advantage: V4 Flash reaches 37.0\% with Direct, 24.4\% with Plan-first, and 23.8\% with Spec-first; V4 Pro reaches 14.2\%, 18.0\%, and 13.6\%, respectively. Spec-first still has the highest CC-F1 in both models (61.9 for Flash and 65.3 for Pro), but the execution channel is sensitive to prompt/action budget and output reliability. The token-matched parse gate remains acceptable overall (95.9\% parsed), though Pro spec-first is the weakest cell at 88.6\% parse and 11.4\% fallback. Cross-family slices are configured in \texttt{configs/experiments.yaml}; they require GPT, Claude, and Gemini credentials before they can support cross-provider claims.

\subsection{Parse Transparency}

The full tool-plan run parsed 17,080 of 18,000 calls cleanly (94.9\%); 920 rows used deterministic repair or fallback paths. The weakest cell is DeepSeek V4 Pro spec-first, with 71.9\% parse and 28.1\% fallback. We report parse transparency beside model scores and avoid treating fallback-heavy cells as clean capability estimates. The parse table is exported to \texttt{paper/tables/parse\_transparency\_full\_toolplan.csv}.

\subsection{Task and Near-Miss Validation}

After the full run, a stricter audit found reference-artifact issues outside the first repaired queue, so we regenerated the full 600-task corpus with the repaired generator. Strict validation now reports 600 / 600 tasks passing reference replay, DoneSpec acceptance on the executed reference final state, near-miss rejection, and domain-specific coverage. The full corpus contains 3,600 near-miss states across 15 mutation taxa. The near-miss breakdown tables are in \texttt{paper/tables/near\_miss\_by\_taxon\_full\_toolplan.csv} and \texttt{paper/tables/near\_miss\_by\_family\_full\_toolplan.csv}.

\subsection{Cost and Runtime}

The full DeepSeek tool-plan run used 18,000 API calls, 8.30M input tokens, and 23.08M output tokens, with an estimated API cost of \$13.47 under the configured price sheet. Summed provider latency was 490,355 seconds; wall-clock runtime depends on concurrency and retry behavior, so we report the resumable command and raw diagnostics rather than a single portable wall-clock number.
